\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{
  top=.5in,
  left=1.25in,
  right=.5in,
  bottom=.5in,
}
\usepackage{changepage}

\newlength{\marginlen}
\newlength{\marginsep}
\newlength{\barlen}
\setlength{\marginlen}{0.75in}
\setlength{\marginsep}{0.05in}
\addtolength{\barlen}{\marginlen}
\addtolength{\barlen}{-\marginsep}


\usepackage[HTML]{xcolor}
\definecolor{barColor}{HTML}{05827c}

\usepackage{titlesec}
\titleformat{\section}%
	{\Large}{}% no label
	{0pt}%
	{% The bar styling
		\color{barColor}%
		\hspace*{-\marginlen}%
		\raise0.25ex\hbox{\rule{\barlen}{1ex}}\hspace{\marginsep}%
	}
\setcounter{secnumdepth}{0} % no section numbering
\titlespacing*{\section}{0pt}{0.5ex}{0.5ex}

\pagestyle{empty}

\usepackage{ebgaramond}
\usepackage{enumitem}
\setlist[itemize]{left=0pt, nosep, before=\small, after=\normalsize, topsep=2pt}

\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks, allcolors=black}

\makeatletter
\newcommand{\email}[1]{\gdef\@email{#1}}
\newcommand{\objective}[1]{\gdef\@objective{#1}}
\newcommand{\linkedin}[1]{\gdef\@linkedin{#1}}
\newcommand{\github}[1]{\gdef\@github{#1}}
\newcommand{\phone}[1]{\gdef\@phone{#1}}

\renewcommand{\maketitle}{
    \begin{adjustwidth}{-\marginlen}{0pt}
        \begin{tabular}{@{} p{0.5\linewidth} @{} p{0.5\linewidth} @{} }
        {
            \fontsize{36}{56}\selectfont \@title 
            \newline
            \fontsize{16}{0}\selectfont \@objective   
        }
        &    
        \parbox{\linewidth}{%
            \raggedleft\large%
            \href{mailto:\@email}{\@email}\par%
            \href{https://\@github}{\@github}\par%
            \href{https://linkedin.com/\@linkedin}{\@linkedin}\par%
            \href{tel:\@phone}{\@phone}\par%
        }
        \end{tabular}
    \end{adjustwidth}
}
\makeatother

\setlength{\parindent}{0pt}

\newcommand{\accentcolor}{blue!50!black!100!white}

\title{Bobby Dhanoolal}
\objective{Seeking 2025 Full Time Position in Backend}
\email{bobbydhanoolal@mail.rit.edu}
\linkedin{in/bobby-dhanoolal}
\github{github.com/bobbykdhan}
\phone{914 409-7471}

\reversemarginpar
\newcommand{\mpar}[1]{\leavevmode\marginpar{\raggedleft #1}}

\begin{document}
\maketitle

\section{Experience}

\mpar{May 2024 --\par Aug 2024}
\textbf{Software Engineer Intern - AI and Automation}, \emph{IBM}
\begin{itemize}
  \item Researched and developed a process to evaluate large language models using AI-created Ontology.
  \item Met with team members to coordinate data analysis to extract information from an IT product's documentation.
  \item \textit{Technologies: Python, SpaCy, Pandas, Numpy, PyTorch.}
\end{itemize}

\smallskip

\mpar{May 2023 --\par Dec 2023}
\textbf{Software Engineering Co Op}, \emph{Codonics}
\begin{itemize}
  \item Investigated and repaired issues regarding the Safe Label System and its Administration Tool.
  \item Coordinated with team members to execute a comprehensive testing workflow aimed at preventing production bugs.
  \item Implemented WiFi 6 technology, resulting in substantial improvements in connectivity speeds and reliability. Proactively managed drivers across diverse adapters.
  \item \textit{Technologies: Java, Bash, Linux, Jenkins, Groovy, C, JavaScript, HTML, Spring.}
\end{itemize}

\smallskip

\mpar{Jan 2022 --\par Dec 2022}
\textbf{Web \& Email Technologist}, \emph{RIT Univ. Advancement}
\begin{itemize}
  \item Created and updated content on the university's Alumni websites using Drupal.
  \item Collaborated with team members using Airtable and Blackbaud to create and process communication emails and email lists.
  \item \textit{Technologies: Drupal, HTML, CSS, Blackbaud, Airtable.}
\end{itemize}

\section{Projects}
\mpar{Feb 2022 --\par Present}
\textbf{Play Tracker, Closed Source}
\begin{itemize}
  \item Integrated Google Cloud services for real-time data retrieval and decision-making.
  \item Built an asynchronous workflow with Python’s Asyncio to optimize trade execution speed.
  \item \textit{Technologies: Python, IBKR API, Docker, Fast API, Google Cloud, Twilio, MySQL.}
\end{itemize}

\smallskip
\mpar{Mar 2025 --\par Present}
\textbf{SummerSync, Closed Source}
\begin{itemize}
  \item Led a team to develop an automated scheduling algorithm for the RIT NTID summer transition program, integrating student ability levels with teacher and room availability to optimize placements and reduce conflicts.
  \item \textit{Technologies: Python, FastAPI, MySQL, OpenShift.}
\end{itemize}


\smallskip
\mpar{Jan 2022 --\par May 2023}
\textbf{AutoOrder-API, \href{https://github.com/Bobbykdhan/AutoOrder-API}{Bobbykdhan/AutoOrder-API}}
\begin{itemize}
  \item Automated a headless browser to order food from the RIT dining hall.
  \item Enabled users to order using HTTP requests instead of via the command line.
  \item \textit{Technologies: Python, FastAPI, Imgur-API, Docker, OpenShift, Selenium.}
\end{itemize}


\section{Skills}

\mpar{Languages} Python, Java, C, JavaScript, Swift, CSS, Apple Script, Bash, LaTeX, MySQL, Assembly, MIPS, HTML

\smallskip

\mpar{Frameworks} React, Drupal, Selenium, React Native, Playwright

\smallskip

\mpar{Libraries} Pandas, Numpy, Express, Tensorflow, PyTorch, Asyncio

\smallskip

\mpar{Technologies} Google Cloud, OpenShift, Docker, FastAPI, Flask, Web Automation, Stripe,

\section{Education}
\mpar{Sep 2021 --\par May 2025}
\textbf{Rochester Institute of Technology, Rochester, NY} \\
B.S. Computer Science \\
Courses: Large Language Models, Programming Language Concepts, Analysis of Algorithms, Machine Learning, \\
Computer Vision

\section{Extracurriculars \& Leadership}
\mpar{Sep 2021 --\par May 2025}
\textbf{Computer Science House - President}, \emph{csh.rit.edu}
\begin{itemize}
  \item Facilitated connections between the organization and outside companies.
  \item Managed a professional organization of nearly 100 active members and a network of over 700 alumni.
  \item Part of a Living Learning Community of Computer Science, Computer Security, and other technical students.
  \item Organized weekly educational seminars and social events.
\end{itemize}

\smallskip
\mpar{Sep 2022 --\par May 2025}
\textbf{National Society of Black Engineers - Member}, \emph{nsbe.org}
\begin{itemize}
  \item Participated in weekly chapter meetings and social events.
\end{itemize}

\end{document}
